IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/proofs.tex
wording
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
  The base case for derivations
  of length 0 is trivial, allowing
  us to simple chose $|ic2'=ic2|$.  In the step case,
  we split the derivation sequence from~\eqref{eq:tsni-lhs} of length $n+1$ as follows:
  \[
  |ic1| |.->| |ic1''| |.->|^n |ic1'|
  \]
  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general} to
  the first step and
  the induction hypothesis to the rest of the derivation sequence,
  we directly get the desired property.
  % long version
%  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
%  The base case for derivations
%  of length 0 is trivial, allowing
%  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
%  the theorem holds for derivation sequences of length up to $n$, and show that it also
%  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
%  \[
%  |ic1| |.->| |ic1''| |.->|^n |ic1'|
%  \]
%  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
%  |ic''| with
%  \begin{equation} \label{eq:tsni-proof-1}
%  |ic1''| \approx_{|il|} |ic2''|
%  \qquad \text{and} \qquad
%  |ic2| |.->|^* |ic2''|
%  \end{equation}
%  Applying the induction hypothesis to
%  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
%  \begin{equation} \label{eq:tsni-proof-2}
%  |ic1'| \approx_{|il|} |ic2'|
%  \qquad \text{and} \qquad
%  |ic2''| |.->|^* |ic2'|
%  \end{equation}
%  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
%  us the right-hand side of the implication in the TSNI
%  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
\end{proof}
\begin{proof}[Proof sketch of Lemma~\ref{lemma:rr-tsni-general}]
  For space reasons, we only sketch the structure of the proof here,
  and refer the interested reader to the appendix where we give the
  full proof.
  The proof distinguishes two cases:
  \begin{itemize}
    \item If the task |it1| executed in |ic1| is erased, then there is no
    need to take a step in |ic2|, as the computation in |ic1| does
    not have any visible effects after erasure.
    \item Otherwise, there must be a corresponding task |it2| in |ic2|, and
    it can take exactly the same reduction step as the task in |ic1|.
    The only difficulty is that there might be secret tasks executing
    before |it2|, but it can be shown that these do not influence the
    computation after erasure.
  \end{itemize}
\end{proof}
The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely
in the same fashion as for Theorem~\ref{thm:iso-tsni} (TSNI), except that
some cases are simpler due to the fact termination is not an issue
(cf.~\cite{lio} for a TINI proof of a similar system).

>>>>

\begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
  The base case for derivations
  of length 0 is trivial, allowing
  us to simple chose $|ic2'=ic2|$.  In the step case,
  we split the derivation sequence from~\eqref{eq:tsni-lhs} of length $n+1$ as follows:
  \[
  |ic1| |.->| |ic1''| |.->|^n |ic1'|
  \]
  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general} to
  the first step and
  the induction hypothesis to the rest of the derivation sequence,
  we directly get the desired property.
  % long version
%  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
%  The base case for derivations
%  of length 0 is trivial, allowing
%  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
%  the theorem holds for derivation sequences of length up to $n$, and show that it also
%  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
%  \[
%  |ic1| |.->| |ic1''| |.->|^n |ic1'|
%  \]
%  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
%  |ic''| with
%  \begin{equation} \label{eq:tsni-proof-1}
%  |ic1''| \approx_{|il|} |ic2''|
%  \qquad \text{and} \qquad
%  |ic2| |.->|^* |ic2''|
%  \end{equation}
%  Applying the induction hypothesis to
%  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
%  \begin{equation} \label{eq:tsni-proof-2}
%  |ic1'| \approx_{|il|} |ic2'|
%  \qquad \text{and} \qquad
%  |ic2''| |.->|^* |ic2'|
%  \end{equation}
%  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
%  us the right-hand side of the implication in the TSNI
%  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
\end{proof}
\begin{proof}[Proof sketch of Lemma~\ref{lemma:rr-tsni-general}]
  For space reasons, we only sketch the structure of the proof here.
  We refer the interested reader to the Appendix for a full proof.
  The proof distinguishes two cases:
  \begin{itemize}
    \item If the task |it1| executed in |ic1| is erased, then there is no
    need to take a step in |ic2|, as the computation in |ic1| does
    not have any visible effects after erasure.
    \item Otherwise, there must be a corresponding task |it2| in |ic2|, and
    it can take exactly the same reduction step as the task in |ic1|.
    The only difficulty is that there might be secret tasks executing
    before |it2|, but it can be shown that these do not influence the
    computation after erasure.
  \end{itemize}
\end{proof}
The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely
in the same fashion as for Theorem~\ref{thm:iso-tsni} (TSNI), except that
some cases are simpler due to the fact termination is not an issue
(cf.~\cite{lio} for a TINI proof of a similar system).
